Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-07-04 PandaOverview.tex
minor in Section II.

PanDA is a Workload Management System (WMS)%~\cite{marco2009glite} 
designed to support the execution of distributed workloads and workflows via
pilots~\cite{turilli2015comprehensive}. Pilot-capable WMS enable high
throughput of tasks execution via multi-level scheduling while supporting
interoperability across multiple sites. This is particularly relevant for LHC
experiments, where millions of tasks are executed across multiple sites every
month, analyzing and producing petabytes of data. 
% The design of PanDA WMS started in 2005 to support ATLAS\@. PanDA went into
% production for the LHC Run 1 on 2009, and was then extended with new
% subsystems for Run 2 in 2015.

@@

Meanwhile, AutoPyFactory defines PanDA Pilots, submitting them to a Condor-G
agent (Fig.~\ref{fig:architecture}:9). Condor-G schedules these pilots
wrapped as jobs or VMs to the required sites
(Fig.~\ref{fig:architecture}:10).

@@

Upon receiving a job, a PanDA Pilot starts a monitoring process and forks a
subprocess for the execution of the job's payload. Input data are transferred
from the stage-in location (Fig.~\ref{fig:architecture}:13) and the job's
payload is executed (Fig.~\ref{fig:architecture}:14). Once completed, output
is transferred to the staging-out location (Fig.~\ref{fig:architecture}:15).

>>>>

PanDA is a Workload Management System (WMS) %~\cite{marco2009glite} 
designed to support the execution of distributed workloads and workflows via
pilots~\cite{turilli2015comprehensive}. Pilot-capable WMS enable high
throughput execution of tasks via multi-level scheduling while supporting
interoperability across multiple sites. This is particularly relevant for LHC
experiments, where millions of tasks are executed across multiple sites every
month, analyzing and producing petabytes of data. 
% The design of PanDA WMS started in 2005 to support ATLAS\@. PanDA went into
% production for the LHC Run 1 on 2009, and was then extended with new
% subsystems for Run 2 in 2015.

@@

Meanwhile, AutoPyFactory defines PanDA Pilots, submitting them to a Condor-G
agent (Fig.~\ref{fig:architecture}:9). Condor-G schedules these pilots
wrapped as jobs to the required sites
(Fig.~\ref{fig:architecture}:10).

@@

A PanDA Pilot starts a monitoring process on receiving a job and forks a
subprocess to execute the job's payload. Input data are transferred
from the stage-in location (Fig.~\ref{fig:architecture}:13), the job's
payload is executed (Fig.~\ref{fig:architecture}:14) and once completed, output
is transferred to the staging-out location (Fig.~\ref{fig:architecture}:15).
